\documentclass{article}
\oddsidemargin=.15in
\evensidemargin=.15in
\textwidth=6in
\topmargin=-.5in
\textheight=9in
\parindent=0in
\usepackage{hyperref}

\pagestyle{empty}
\begin{document}

\begin{center}
{\Large Emile Takahiro Okada} \\[.5pc]
National University of Singapore, Department of Mathematics \\
okada\verb|@|nus.edu.sg \\
(+65)86272506\\[5pc]
\end{center}

{\large \bf Academic Positions} \\*[-.8pc]
\underline{\hspace{1.7in}}
\\
 {\bf 2022-Current}: Peng Tsu Ann Assistant Professor, National University of Singapore \\
\\
{\large \bf Education} \\*[-.8pc]
\underline{\hspace{0.9in}}
\\
{\bf 2018-2022: DPhil in Mathematics, University of Oxford} \\
Thesis: The wavefront set of representations of $p$-adic groups \\
Supervisors: Prof. Dan Ciubotaru, Prof. Kevin McGerty\\
\\
{\bf 2017-2018: Master of Mathematics, University of Cambridge} \\
Thesis: Modular Representations of Finite Groups of Lie Type in the Defining Characteristic. \\
Grade: Distinction. \\
\\
{\bf 2014-2017: Bachelor of Arts in Mathematics, University of Cambridge} \\
Grade: First Class in all years. \\
\\
{\large \bf Skills} \\*[-.8pc]
\underline{\hspace{0.5in}} \\
{\bf Computer Languages} \\
Python, Matlab, C++, Mathematica, GAP, \LaTeX, HTML, JavaScript, CSS. \\
\\
{\bf Languages} \\
Fluent in English and Norwegian. Conversant in Japanese.
\\
\\
{\large \bf Publications} \\*[-.8pc]
\underline{\hspace{1.1in}} 
\\
8. \textbf{The stable wave front set of the theta representation} \\% \hfill {\it 2024\/} \\
\textit{with E. Karasiewicz, R. Wang} \\
submitted. \\
%in preparation.  \\
\\
7. \textbf{Ramification of weak Arthur packets for p-adic groups} \\% \hfill {\it 2024\/}\\
\textit{with M. Gurevich}, \\
%77 pages, 
submitted. \\
%\href{https://arxiv.org/abs/2404.03485}{https://arxiv.org/abs/2404.03485} \\
\\
6. \textbf{Local character expansions and asymptotic cones over finite fields} \\% \hfill {\it 2023\/} \\
\textit{with D. Ciubotaru}, \\
%16 pages, 
Proceedings of the London Mathematical Society (accepted). \\
%\href{https://arxiv.org/abs/2307.06780}{https://arxiv.org/abs/2307.06780} \\
\\
5. \textbf{Wavefront Sets of Unipotent Representations of Reductive $p$-adic Groups II} \\% \hfill {\it 2023\/}\\
\textit{with D. Ciubotaru, L. Mason-Brown}, \\
%55 pages, 
Journal für die reine und angewandte Mathematik (accepted) \\
%\href{https://arxiv.org/abs/2303.10713}{https://arxiv.org/abs/2303.10713}  \\
\\
4. \textbf{Some Unipotent Arthur Packets for Reductive p-adic Groups} \\ %\hfill {\it 2022\/} \\
\textit{with D. Ciubotaru, L. Mason-Brown}, \\
%18 pages, 
International Mathematics Research Notices, Volume 2024, Issue 9, May 2024, Pages 7502–7525 \\
%\href{https://arxiv.org/abs/2210.00251}{https://arxiv.org/abs/2210.00251} \\
\\
3. \textbf{The Wavefront Sets of Unipotent Supercuspidal Representations}, \\%\hfill {\it 2022\/}\\
\textit{with D. Ciubotaru, L. Mason-Brown}, \\
%20 pages, 
Algebra \& Number Theory, Vol. 18 (2024), No. 10, 1863–1889 \\
%\href{https://arxiv.org/abs/2206.08628}{https://arxiv.org/abs/2206.08628} \\
\\
2. \textbf{Wavefront Sets of Unipotent Representations of Reductive $p$-adic Groups I} , \\%\hfill {\it 2021\/}\\
\textit{with D. Ciubotaru, L. Mason-Brown}, \\
%44 pages, 
American Journal of Mathematics (accepted) \\
%\href{https://arxiv.org/abs/2112.14354}{https://arxiv.org/abs/2112.14354}  \\
\\
1. \textbf{The wavefront set of representations of p-adic groups}, \\%\hfill {\it 2021\/} \\
%60 pages, 
PhD thesis \\
%\href{https://arxiv.org/abs/2107.10591}{https://arxiv.org/abs/2107.10591}  \\
\\
\\
{\large \bf Invited Talks} \\*[-.8pc]
\underline{\hspace{1.2in}} 
\\
{\it 
On Lusztig’s local Langlands correspondence and functoriality}, Xiamen University, China. \hfill {\it 01/2025\/} \\
\\
{\it 
An introduction to the representation theory of p-adic groups}, Xiamen University, China. \hfill {\it 01/2025\/} \\
\\
{\it 
On Singularities and Ramification of Arthur Packets}, Beijing International Center for Mathematical Research, Peking University, China. \hfill {\it 12/2024\/} \\
\\
{\it 
Involutivity in the unramified local Langlands correspondence}, Yau Mathematical Sciences Center at Beijing, Tsinghua University, China. \hfill {\it 12/2024\/} \\
\\
{\it 
On the Adams--Vogan conjecture}, NCTS Workshop on Representation Theory and Lie Groups, National Center for Theoretical Sciences, Taiwan. \hfill {\it 12/2024\/} \\
\\
{\it 
Types, Hecke algebras, and wave front sets}, Representations of $p$-adic groups, Mathematisches Forschungsinstitut Oberwolfach, Germany. \hfill {\it 12/2024\/} \\
\\
{\it 
Lecture series on the wave front set (4 lectures)}, National University of Singapore, Singapore. \\
$\hphantom{ }$ \hfill {\it 11/2024\/} \\
\\
{\it 
Character sheaves, Hecke algebras, and the wavefront set}, Representation theory seminar, University of Melbourne, Australia. \hfill {\it 08/2024\/} \\
\\
{\it 
Ramification of weak Arthur packets}, Pan Asian Number Theory Conference, Vietnam Institute of Advanced Study in Mathematics, Vietnam. \hfill {\it 07/2024\/} \\
\\
{\it 
Ramification of weak Arthur packets}, Algebra seminar, University of Aarhus, Denmark. \hfill {\it 07/2024\/} \\
\\
{\it 
Ramification of weak Arthur packets}, Pacific Rim Conference in Mathematics, Darwin, Australia. \hfill {\it 06/2024\/} \\
\\
{\it 
The wavefront set of a p-adic representation}, Lie Theory seminar, Chinese University of Hong Kong, Shenzhen, China. \hfill {\it 04/2024\/} \\
\\
{\it 
Weakly spherical representations and the weak Arthur packet conjecture}, Arthur Packets, Institute for Advanced Study in Mathematics, Hangzhou, China. \hfill {\it 11/2023\/} \\
\\
{\it 
On some recent progress on wavefront sets in depth-0 and positive depth}, Anaparastaseis: Orbits, Hecke algebras, and representations, Nisyros. \hfill {\it 07/2023\/} \\
\\
{\it 
The wavefront set of unipotent representations with real infinitesimal character}, Algebra Seminar, Oxford University. \hfill {\it 06/2023\/} \\
\\
{\it The wavefront set of unipotent representations with real infinitesimal character}, Algebra University, Haifa University. \hfill {\it 05/2023\/} \\
\\
{\it 
Wavefront sets of representations of p-adic groups}, Mini-workshop on $p$-adic group representations, Fudan University. \hfill {\it 12/2022\/} \\
\\
{\it 
New results and open questions from the study of local wavefront sets}, Representation Theory and Number Theory Seminar, National University of Singapore. \hfill {\it 09/2022\/} \\
\\
{\it 
On the construction of some unipotent local Arthur packets}, Minimal Representations and Theta Correspondence, Erwin Schr{\"o}dinger International Institute for Mathematics and Physics. \hfill {\it 02/2022\/} \\
\\
{\it 
The wavefront set and Arthur packets of p-adic groups}, Lie Groups Seminar, MIT. \hfill {\it 02/2022\/} \\
\\
{\it Arthur packets for p-adic groups and the wavefront set}, Number Theory Seminar, University of Cambridge. \hfill {\it 02/2022\/} \\
\\
{\it The wavefront set of representations of p-adic groups}, Algebraic Geometry and Representation Theory Seminar, Weizmann Institute. \hfill {\it 01/2022\/} \\
\\
{\it The Wavefront Set of Spherical Arthur Representations}, Representation Theory Seminar, Purdue University. \hfill {\it 10/2021\/} \\
\\
{\it The wavefront set of admissible representations of p-adic groups}, Representations of $p$-adic groups and related topics, Durham University. \hfill {\it 09/2021\/} \\
\\
{\it The Wavefront Set of Spherical Arthur Representations}, Representation Theory and Number Theory Seminar, National University of Singapore. \hfill {\it 09/2021\/} \\
\\
{\it  
Parameterising unramified nilpotent orbits using dual Springer parameters}, Algebra Seminar, University of Oxford. \hfill {\it 10/2020\/} \\
\\
{\it A parameterisation of nilpotent orbits over a maximal unramified extension of a p-adic field using dual Springer parameters}, Junior London Algebra Colloquium, Imperial College London. \hfill {\it 07/2020\/} \\
\\
\\
{\large \bf Conferences} \\*[-.8pc]
\underline{\hspace{1.2in}} \\
%{\bf NCTS Workshop on Representation Theory and Lie Groups} \hfill {\it December 2024 \/} \\
%National Center for Theoretical Sciences, Taiwan. 1 week.\\
{\bf Representations of $p$-adic groups} \hfill {\it December 2024 \/} \\
Mathematisches Forschungsinstitut Oberwolfach, Germany. 1 week.\\
{\bf Representation Theory and Lie Groups} \hfill {\it October 2024 \/} \\
Brin Mathematics Research Center, United States of America. 1 week.\\
{\bf Pan Asian Number Theory Conference} \hfill {\it July 2024 \/} \\
Vietnam Institute of Advanced Study in Mathematics, Vietnam. 1 week.\\
{\bf Pacific Rim Conference in Mathematics} \hfill {\it June 2024 \/} \\
Australian National University, Australia. 1 week.\\
{\bf Arthur Packets} \hfill {\it November 2023 \/} \\
Institute for Advanced Study in Mathematics, Hangzhou, China. 1 week.\\
{\bf Anaparastaseis: Orbits, Hecke algebras, and representations} \hfill {\it July 2023 \/} \\
Nisyros, Greece. 1 week.\\
{\bf Representation Theory, Combinatorics and Geometry} \hfill {\it December 2022 \/} \\
National University of Singapore, Singapore. 4 weeks.\\
{\bf Minimal Representations and Theta Correspondence} \hfill {\it April 2022 \/} \\
Erwin Schr{\"o}dinger International Institute for Mathematics and Physics, Austria. 1 weeks.\\
{\bf Representations of $p$-adic groups and related topics} \hfill {\it September 2021 \/} \\
Durham University, Durham, UK. 1 day.\\
{\bf Buildings and Affine Grassmannians } \hfill {\it August 2019 \/} \\
Centre International de Rencontres Mathématiques, Marseille, France. 2 weeks.\\
\\
\\
{\large \bf Teaching} \\*[-.8pc]
\underline{\hspace{0.9in}} \\
{\bf Lecturer - National University of Singapore}  \\
MA5211 Lie Theory, MA3201 Algebra II. \\
\\
{\bf Tutor - Somerville College, University of Oxford}  \\
Prelims Analysis II, Prelims Analysis III, Part A Integration, Part A Topology, and Part A Groups. \\
\\
%MA5211 Lie Theory, MA3201 Algebra II. \\\\
{\bf Teaching Assistant - Mathematical Institute, University of Oxford}  \\
%MA5211 Lie Theory, MA3201 Algebra II. \\
B2.1 Introduction to Representation Theory (x2), B2.2 Commutative Algebra (x1), B3.1 Galois Theory (x4), C2.2 Homological Algebra (x1), C2.7 Category Theory (x1).\\
\\
%{\large \bf Mentorship } \\*[-.8pc]
%\underline{\hspace{1.1in}} \\
{\bf Master's students}  \\
{Timothy Peck Hsien Wei} \hfill {\it 2023 - 2024 \/} \\
\\
{\bf Undergraduate research project}  \\
{Galileo Grey} \hfill {\it 2024 - current \/} \\
\\
\\

{\large \bf Service} \\*[-.8pc]
\underline{\hspace{0.9in}} \\
{\bf Journal Referee}  \\
Selecta Mathematica, Advances in Mathematics, Algebra and Number Theory, International Mathematics Research Notices.\\
\\
{\bf Seminar Organiser}  \\
Algebraic groups \hfill {\it 2019} \\
The local Langlands correspondence for unipotent representations \hfill {\it 2022}\\
$p$-adic Arthur packets \hfill {\it 2024}\\
\\
\\

{\large \bf Awards and Honors} \\*[-.8pc]
\underline{\hspace{1.8in}} \\
{\bf Aker Scholarship} \hfill {\it 2018 - 2022\/} \\
{\bf Cambridge University Trust Scholarship} \hfill {\it 2014 - 2018\/} \\
{\bf Emmanuel College Examination Prizes} \hfill {\it 2015,2016,2017,2018} \\
%Braithwaite Batty Senior Scholar \hfill {\it 2015, 2016 2017\/} \\
%Honorary Bachelor Scholarship \hfill {\it 2018} \\
%Rowley Mainhood Prize \hfill {\it 2015, 2016} \\
\\
\\
\\
{\large\bf Employment} \\*[-.8pc]
\underline{\hspace{1.4in}} 
\\
\\
{\bf University of Oxford} \\*[-.8pc]
\underline{\hspace{1.7in}} \\
{\bf Stipendiary Lecturer at Somerville College} \hfill {\it January 2021-September 2021\/} \\
%Tutor for Prelims Analysis II, Prelims Analysis III, Part A Integration, Part A Topology, and Part A Groups. \\
\\
%{\bf Teaching Assistant} \hfill {\it 2018-2020\/} \\
%B2.1 Introduction to Representation Theory (x2), B2.2 Commutative Algebra (x1), B3.1 Galois Theory (x4), C2.2 Homological Algebra (x1), C2.7 Category Theory (x1).\\
{\bf Den Norske Bank (DNB Bank ASA)} \\*[-.8pc]
\underline{\hspace{2.7in}} 
\\
{\bf Foreign Exchange Desk Intern} \hfill {\it July - August 2018\/} \\
%Used reinforcement learning to develop highly profitable trading algorithm for the foreign exchange market.\\
%\\
{\bf Digitalization, Business Development and Innovation Intern} \hfill {\it June - September 2017\/} \\
%Developed machine learning algorithms for churn rate prediction and identifying potential customers. \\
\textbf{Awards:} 1st place in hackathon.\\
\\
{\bf Summer Research in Mathematics} \\*[-.8pc]
\underline{\hspace{2.5in}} \\
{\bf Cambridge Image Analysis Group, University of Cambridge} \hfill {\it June - August 2016\/} \\
\\
\\
{\bf Other } \\*[-.8pc]
\underline{\hspace{0.45in}} \\
%Created a shadow tomography device.
%Learned how to create electrical circuits, solder, 3D print, and program a tomography device. Presented device at the Cambridge Science Festival. \\
{\bf Part-Time Developer, Agora} \hfill {\it November 2014 - January 2016 \/} \\
%Implemented new ticketing functionality. Wrote a scraper to gather Cambridge related events. Implemented web landing page.
%Worked remotely and used git and github for version control and to provide weekly project reports. \\
{\bf Part-Time Research Assistant, Kyoto University} \hfill {\it December 2014 - October 2015\/} \\
%Implemented quantum algorithms for interger factorisation and Ramsey number determination on the D-Wave computer.
%Developed preprocessing schemes to improve performance.
%Worked with large computing clusters and obtained a strong command of the unix terminal. \\
Supervisor: Dr. Nike Dattani. \\
\\
\\
%{\large \bf Interests} \\*[-.8pc]
%\underline{\hspace{6in}} \\
%\\
%Squash, football, badminton, chess, guitar. \\
%\\
{\large \bf References} \\*[-.8pc]
\underline{\hspace{6in}} \\
{\bf Dan Ciubotaru}, University of Oxford,  \hfill {\it dan.ciubotaru@maths.ox.ac.uk \/} \\
{\bf Wee Teck Gan}, National University of Singapore,  \hfill {\it matgwt@nus.edu.sg \/} \\
%{\bf Kari Vilonen}, The University of Melbourne,  \hfill {\it kari.vilonen@unimelb.edu.au \/} \\
{\bf Maxim Gurevich}, Technion - Israel Institute of Technology,  \hfill {\it maxg@technion.ac.il \/} \\
{\bf Lucas Mason-Brown}, The University of Texas at Austin,  \hfill {\it lucas.masonbrown@gmail.com \/} \\
%Mathematical Institute,
%University of Oxford,
%Andrew Wiles Building,
%Radcliffe Observatory Quarter,
%Woodstock Road,
%Oxford,
%OX2 6GG.
%\\
%{\bf Kevin McGerty}  \hfill {\it Kevin.Mcgerty@maths.ox.ac.uk \/} \\
%Mathematical Institute,
%University of Oxford,
%Andrew Wiles Building,
%Radcliffe Observatory Quarter,
%Woodstock Road,
%Oxford,
%OX2 6GG.
%{\bf Stephen J. Cowley}  \hfill {\it S.J.Cowley@emma.cam.ac.uk \/} \\
%Centre for Mathematical Sciences,
%Wilberforce Road,
%Cambridge,
%CB3 0WA,
%United Kingdom \\
%Director of Studies at Emmanuel College, University of Cambridge. \\
%\\




\end{document}

%My primary interest is in the wavefront set of irreducible admissible representations of p-adic groups and its relation to the local Langlands correspondence. I am also interested in its relation to Fourier coefficients of automorphic forms, Arthur packets, and unitary representations. Through the tools I use I am also interested in character sheaves, affine/graded Hecke algebras and harmonic analysis on p-adic groups.